Parallel Solving of Multiple Information-Coordinated Global Optimization Problems

### 2021-03-03 2020/JPDC_MCO/2020_JPDC.tex
1. JPDC поправлен список литературы

\begin{abstract}
This paper proposes an efficient approach for the parallel solution of computationally time consuming problems of multiple global optimization problems, in which minimized functions can be multiextremal and calculating function values may require huge amounts of computations. The proposed approach is based on the information-statistical theory of global optimization, at which a general computational scheme of global optimization methods is proposed. In the paper, this general scheme is expanded by the possible reuse of search information obtained in the process of computations when solving multiple global optimization problems. Within the framework of the proposed generalized scheme, parallel algorithms are proposed for computational systems with shared and distributed memory. Results of computational experiments demonstrated that the proposed approach can significantly reduce the computational complexity of solving multiple global optimization problems.
\end{abstract}

\begin{keyword}
Global optimization\sep dimensionality reduction\sep search information\sep parallel methods of global search\sep computational complexity.
\end{keyword}

@@

Global optimization (GO) problems are among the most complex optimization problems. In contrast to local optimization problems, when searching for a global minimum, the numerical method must evaluate the behavior of the optimized function in the entire global search area. In general, GO problems are subject to the ``dimensionality curse'', when the volume of computations performed increases exponentially with increasing dimensionality. Such computational complexity, as well as high practical demand, have led to a great deal of research activity in the field of global optimization. As a result of this research, numerous effective methods for solving global optimization problems and examples of solving practical problems have been proposed -- see, for example, \cite{c1,c2,c3,c4,c5,c6,c7,c8,c9,c10,c11,c12,c13,c14,c18}.

>>>>

\begin{abstract}
This paper proposes an efficient approach for the parallel solution of computationally time consuming problems of multiple global optimization, in which minimized functions can be multiextremal and calculating function values may require huge amounts of computations. The proposed approach is based on the information-statistical theory of global optimization, within which a general computational scheme of global optimization methods is proposed. In the paper, this general scheme is expanded by the possible reuse of search information obtained in the process of computations when solving multiple global optimization problems. Within the framework of the proposed generalized scheme, parallel algorithms are proposed for computational systems with shared and distributed memory. Results of computational experiments demonstrated that the proposed approach can significantly reduce the computational complexity of solving multiple global optimization problems.
\end{abstract}

\begin{keyword}
Global optimization \sep dimensionality reduction \sep search information \sep parallel methods of global search \sep computational complexity.
\end{keyword}

@@

\cite{c1,c2,c3,c4,c5,c6,c7,c8,c9,c10}
\cite{c11,c12,c13,c14,c15,c16,c17,c18,c19,c20}
\cite{c21,c22,c23,c24,c25,c26,c27,c28,c29,c30}
\cite{c31,c32,c33,c34,c35,c36,c37,c38,c39,c40,c41}

Since the early 1960s, the problems of global optimization (GO) have continued to be a grand challenge to the theory and practice of optimization. In contrast to local optimization problems, when searching for a global minimum, the numerical method must evaluate the behavior of the function to be optimized in the entire global search domain. In general, GO problems are subject to the ``dimensionality curse'', when the volume of computations performed increases exponentially with increasing dimensionality. Such computational complexity, as well as high practical demand, have led to a great deal of research activity in the field of global optimization. An overview of approaches developed for solving global optimization problems is presented, for example, in a number of recent monographs and reviews -- see \cite{c1,c2,c3,c4,c5,c6,c7,c8,c9}.
